---
title: "Activity: Street or Road?"
author: "YOUR NAME HERE"
output: html_notebook
---

## Load in the data

```{r}
#load libraries 

#load in the data here 
# we will only be using the "street-addresses.csv" file from the text



```

## Recreate Solved Example using `sample(50)`

```{r}


```

## Recreate Soved Example using the entire `Address` data set

```{r}


```

#### Additional Question: How many addresses are a PO BOX (including NCSU BOX)? 

```{r}


```

My answer here...... 


## Back to the Streets: Your Turn

#### Part 1: Explain (in english) each line of the following code chunk

```{r}
pattern <- "(ST|RD|ROAD)"
LeftOvers <-
  Addresses %>% 
  filter( !grepl(pattern, address),
          !grepl("\\sAPT|UNIT\\s[\\d]+$", address),
          !grepl(" BOX ", address)
          )
```

My answer here.......

#### Part 2: Implement your method on the entire `Addresses` data set. Explain how your code works line by line.

```{r}



```

My answer here.......

#### Additional Question 1: Present your result from part 2 by providing a table in descending order of popularity for the street name endings you found

```{r}


```

#### Additional Question 2: Present your result by using ggplot to a bar chart in descending order of popularity for the street name endings you found previously.

Note: make sure your order street names according to popularity, not alphabetically.

```{r}

```

#### Additional Question 3: Comment on any patterns you see

My answer here.......
