---
title: "Activity: Street or Road?"
author: "Mia Iceland"
output: html_notebook
---

## Load in the data

```{r}
#load libraries 
library(tidyverse)

#load in the data here 
# we will only be using the "street-addresses.csv" file from the text

Address <- read_csv("https://mdbeckman.github.io/dcSupplement/data/street-addresses.csv")


```

## Recreate Solved Example using `sample(50)`

```{r}

Sample <- 
  DataTable %>%
  sample_n(size = 50)

Matches <- 
  Sample %>%
  filter(grepl(pattern = "PO", address))

Dont <- 
  Sample %>%
  filter( !grepl(pattern = "PO", address))

```

## Recreate Soved Example using the entire `Address` data set

```{r}

pattern <- "BOX\\s+(\\d+)"

Matches1 <- 
  Address %>% 
  filter(grepl(pattern, address))

Dont1 <-
  Address %>%
  filter( !grepl(pattern, address))

```

#### Additional Question: How many addresses are a PO BOX (including NCSU BOX)? 

```{r}

Matches1 %>%
  summarise(count = n())

```

There are 111,000 addresses that are a PO BOX. 


## Back to the Streets: Your Turn

#### Part 1: Explain (in english) each line of the following code chunk

```{r}
pattern <- "(ST|RD|ROAD)"
LeftOvers <-
  Addresses %>% 
  filter( !grepl(pattern, address),
          !grepl("\\sAPT|UNIT\\s[\\d]+$", address),
          !grepl(" BOX ", address)
          )
```

First Line: is creating a new variable "pattern" and within it identifies the pattern that we are trying to extract. It is grouping all cases that have "ST", "RD", or "ROAD".
Second Line: creating a new data table and labeling it.
Third Line: calling an existing table.
Forth Line: the filter subsets the "Addresses" data set. The conditions within filter():
-do not include cases with the "pattern" in the address column (do not include "ST", "RD", or "ROAD")
-do not include cases with  white space before and after the characters "APT" or "UNIT", followed by any number of digits, with those digits ending the case in the address column
-do not include cases with the characters " BOX" in the address column


#### Part 2: Implement your method on the entire `Addresses` data set. Explain how your code works line by line.

```{r}



```

My answer here.......

#### Additional Question 1: Present your result from part 2 by providing a table in descending order of popularity for the street name endings you found

```{r}


```

#### Additional Question 2: Present your result by using ggplot to a bar chart in descending order of popularity for the street name endings you found previously.

Note: make sure your order street names according to popularity, not alphabetically.

```{r}

```

#### Additional Question 3: Comment on any patterns you see

My answer here.......
